Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-09-01 ms.tex
Starting to rework discussion section

\section{Discussion}
% How can you apply the solution? Talk about it as an application of the problem that justifies going through the effort of implementing it. It reads like an introduction right now, but we can modify it to include less detail.
% Don't explain exactly what hybrid diffusion models are. Remove that paragraph. Put a ref in for Smith and Densmore - lot of applications to speed up lya, including core skipping & hybrid diffusion methods. Another method that's been widely applied is modified random walk methods, but htose require a solution of transfer in a sphere. So, the primary application of this calcuation is to develop that random walk model that will be used in future applicaitons. Keep reference to Ahn et al, since they did basically this but not in spherical symmetry.
% Discussion section: tlak about the differences between what we find and the other results from other papers. Add this as well. 
% First part of discussion - compare to previous work and summarize differences. Move some of the comparison with Dijkstra to the discussion.
% Second part - application of solution
% Move summary to discussion - currently written more like a discussion. 
% Write summary like it's a complement to the abstract. Cliffnotes version for people who don't want to read it.
% We re-examined previous solutions, noting that they use this incorrect boundary conditoin. We re-examined the problem with an appropriate bc, examine spectral and time dpeendence, key results are these, plan to use in a MC acceleration scheme in the future. Comment on comparison with MC. One, maybe two paragraphs.
There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations.  The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}.  These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core. Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.

@@

The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} has been generalized to allow a monochromatic source of photons with frequencies away from line center. A correction to the $J=0$ surface boundary condition which allows the proper condition $J=\sqrt{3}H$ to be satisfied comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$, which are solved using a continuous Fourier expansion in frequency. Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions. In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation. The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth. Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths. Additionally, since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons. Since the peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$, calculations performed at lower optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core. By comparison with Monte Carlo simulations, it is seen that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered, provided a sufficiently large optical depth $\tau_0$.

>>>>

\section{Discussion}
% How can you apply the solution? Talk about it as an application of the problem that justifies going through the effort of implementing it. It reads like an introduction right now, but we can modify it to include less detail.
% Don't explain exactly what hybrid diffusion models are. Remove that paragraph. Put a ref in for Smith and Densmore - lot of applications to speed up lya, including core skipping & hybrid diffusion methods. Another method that's been widely applied is modified random walk methods, but htose require a solution of transfer in a sphere. So, the primary application of this calcuation is to develop that random walk model that will be used in future applicaitons. Keep reference to Ahn et al, since they did basically this but not in spherical symmetry.
% Discussion section: tlak about the differences between what we find and the other results from other papers. Add this as well. 
% First part of discussion - compare to previous work and summarize differences. Move some of the comparison with Dijkstra to the discussion.
% Second part - application of solution

The solution for mean intensity ($J$) and flux ($H = F/4\pi$) of photons near line-center frequency $\nu_0$ in a uniform sphere originally derived by \cite{2006ApJ...649...14D} (called $H_0$ here) has been generalized to allow a monochromatic source of photons with frequencies away from line center, and a correction to the incorrect $J=0$ surface boundary condition is made. This correction allows the proper condition $J=\sqrt{3}H$ to be satisfied, and comes from the introduction of the terms $J_{\rm bc}$ and $H_{\rm bc}$ which are solved using a continuous Fourier expansion in frequency. Enforcement of the correct boundary term leads naturally to expansion of the spatial dependence in terms of spherical Bessel functions. In practice, the continuous expansions are discretized and the Fourier coefficients solved for via a matrix equation. The resulting flux correction, $H_{\rm bc}$, scales as $(a\tau_0)^{-1/3}$ where $a$ is the damping parameter and $\tau_0$ is the line-center optical depth. Thus, for very large optical depths, only a small correction to $H_0$ is needed, while larger errors are present in calculations performed at lower optical depths. Since the Laplacian form of the differential equation is only attainable by approximating the line profile as $\phi \approx a/(\pi x^2)$, these solutions are invalid in areas where the Doppler core of the \lya line has a significant effect on the scattering of photons. The peak of the spectral energy distribution of escaping photons is $x_0 = (a\tau_0)^{1/3}$; as such, calculations performed at low optical depths are likely to be inaccurate due to the close proximity of the spectral peak and the Doppler core of the line profile. By comparison with Monte Carlo simulations, we have shown that the enforcement of the correct frequency-dependent boundary conditions improves the accuracy of these analytic solutions %and correctly tracks changes in the spectrum of escaping photons as the monochromatic source frequency $x_s$ is altered, 
provided a sufficiently large optical depth $\tau_0$. Specifically, this solution shows improvement over previous solutions that utilized a $J=0$ surface boundary condition, such as \cite{1973MNRAS.162...43H}, \cite{1990ApJ...350..216N}, \cite{2006ApJ...649...14D} and others. The surface boundary condition correction $H_{\rm bc}$ is positive in the line wing and negative at the peak of the spectrum, which suggests the previously cited solutions are too large at the spectral peaks and too small further out in the wing. This appears to be the consequence of not enforcing the correct frequency-dependent boundary conditions at the surface of the medium.

The primary application of this solution for resonance-line radiation transfer at large optical depths is to develop a computationally efficient random walk model in spherical geometry. There are several methods that are commonly used to accelerate Monte Carlo radiation transfer calculations. The simplest class of methods that is specific to resonance line transfer are core skipping methods \citep{1968ApJ...153..783A,2002ApJ...567..922A}. These methods focus on Monte Carlo transfer in the wings of the line and avoid scatterings in the core, but

Previous work by \citet{2002ApJ...567..922A,2015MNRAS.449.4336S} discussed Monte Carlo code acceleration for optical depths as large as these in a uniform plane-parallel medium with no absorption, but these calculations would need to be generalized to spherical symmetry in order to construct a model of resonant scattering in exoplanet atmospheres as discussed in Section \ref{sec:intro}.

   Line core photons are pushed to the wings by biasing the atomic velocity distribution to high velocities so the opacity is lower and escape is more rapid.

@@

% Move summary to discussion - currently written more like a discussion. 
% Write summary like it's a complement to the abstract. Cliffnotes version for people who don't want to read it.
% We re-examined previous solutions, noting that they use this incorrect boundary conditoin. We re-examined the problem with an appropriate bc, examine spectral and time dpeendence, key results are these, plan to use in a MC acceleration scheme in the future. Comment on comparison with MC. One, maybe two paragraphs.
